\documentclass[10pt,letterpaper]{article}

% ----- ENCODING -----
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% ----- MARGINS -----
\usepackage[top=0.5in,bottom=0.5in,left=0.45in,right=0.55in]{geometry}

% ----- FONT -----
\usepackage{newtxtext}

% ----- LINKS -----
\usepackage[colorlinks=true,urlcolor=blue,linkcolor=blue]{hyperref}

% ----- LIST CONTROL -----
\usepackage{enumitem}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

% ----- SECTION LINE -----
\newcommand{\sectionline}{
  \vspace{2pt}
  \hrule
  \hrule
  \vspace{6pt}
}

% ----- BULLET SETTINGS -----
\setlist[itemize]{
  label=$\bullet$,
  leftmargin=14pt,
  labelsep=6pt,
  itemsep=2pt,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt
}

\begin{document}

\begin{center}
\textbf{\Large CHARAN CHINTALAPURI}\\
United States \textbar\ +1 (210) 254-8234 \textbar\
\href{mailto:charanreddych6@gmail.com}{charanreddych6@gmail.com}
\textbar\
\href{https://www.linkedin.com/in/charan-reddy-787b72234/}{LinkedIn:Charan Reddy}
\end{center}

\textbf{Summary}
\sectionline

Software Engineer with 4+ years of experience designing, building, and operating distributed cloud-native backend systems. Strong expertise in Java, Spring Boot, microservices, and event-driven architectures with experience delivering highly available and scalable services in healthcare and large-scale e-commerce environments. Skilled in system design, performance optimization, cloud infrastructure, and operational reliability.



\vspace{4pt}
\textbf{Skills}
\sectionline

\textbf{Languages:} Java, C++, JavaScript, TypeScript, SQL

\textbf{Backend \& APIs:} Spring Boot, Microservices, REST APIs, GraphQL, API Versioning, Event-Driven Systems

\textbf{Databases \& Caching:} MySQL, PostgreSQL, SQL Server, Redis, Query Optimization, High Volume Transaction Processing

\textbf{Messaging \& Streaming:} Apache Kafka, Pub/Sub Messaging, Real-Time Data Pipelines

\textbf{Cloud Platforms:} AWS, Microsoft Azure, Cloud Architecture Concepts

\textbf{Containers \& DevOps:} Docker, Kubernetes, Terraform, Jenkins, GitLab CI/CD

\textbf{Testing \& Reliability:} JUnit, Automated Testing, Incident Management, SLI/SLO Monitoring

\textbf{Observability:} Splunk, Centralized Logging, Metrics, Alerting

\textbf{Frontend:} ReactJS, Angular, Redux



\vspace{4pt}
\textbf{Professional Experience}
\sectionline

\textbf{Software Engineer  | Cigna Healthcare} \hfill 07/2024 -- Present\\
\vspace{-12pt}
\begin{itemize}
\item Design, develop, and operate Java Spring Boot microservices processing real-time healthcare and claims data with 99.99\% service availability.
\item Implement Kafka-based event-driven pipelines to synchronize member eligibility and policy data across distributed systems.
\item Build and maintain scalable REST and GraphQL APIs with strong API contract management and backward compatibility.
\item Implement centralized logging, metrics, and alerting using Splunk and cloud monitoring tools, reducing MTTR by approximately 25\%.
\item Optimize MySQL schemas and queries for high-volume pharmacy benefit workflows, improving reporting performance by approximately 30\%.
\item Provision infrastructure using Terraform modules enabling portable deployments across multiple cloud environments.
\item Deploy containerized applications on Kubernetes supporting autoscaling and zero-downtime deployments.
\item Collaborate with cross-functional teams to deliver enterprise SaaS features serving millions of users.
\item Participate in production on-call rotations and lead post-incident reviews to improve system reliability.
\end{itemize}



\vspace{4pt}
\textbf{Software Developer | Flipkart}      \hfill 01/2020 -- 06/2022\\
\vspace{-12pt}
\begin{itemize}
\item Designed and implemented a high-concurrency inventory management service using Java and C++ supporting hundreds of thousands of requests per second.
\item Refactored legacy monolithic systems into Spring Boot microservices reducing deployment cycles by approximately 35\%.
\item Built event-driven order processing pipelines using Apache Kafka improving system resilience and fault isolation.
\item Implemented Redis caching layers to reduce latency and database load during high traffic events.
\item Designed high availability database architectures using PostgreSQL and SQL Server.
\item Developed operational dashboards using Angular and Redux providing real-time visibility into logistics workflows.
\item Implemented CI/CD pipelines using Jenkins and automated testing with JUnit achieving high code coverage.
\item Migrated synchronous service communication to Kafka-based asynchronous messaging improving scalability.
\item Authored technical documentation and API schemas to accelerate onboarding for new engineers.
\item Improved platform security through MFA and enhanced session management.
\end{itemize}



\vspace{4pt}
\textbf{Certifications}
\sectionline

Oracle Certified Associate (OCA) -- Java SE Programmer\\
Azure Developer Associate



\vspace{4pt}
\textbf{Education}
\sectionline

\textbf{Master of Science: Computer Science} \hfill 05/2024\\
Wichita State University, Wichita, KS, USA

\end{document}